MCR_Algae_Data_Cleaning

### 2024-05-03 MCR_Algae_Data_Cleaning.Rmd
updated cleaning to identify which transects are missing quads after filtering

@@

@@

#yay, they are the same 85 
```

@@

## Anything below this line was to help identify missing data, overall taxa levels, etc. and does not need to be run to get a cleaned dataframe

@@

### NOTE - USED CHAT GPT FOR THIS NEXT PART
# Step 1: Create a contingency table of counts for each combination of year and site
year_site_counts <- table(algae_wide$Year, algae_wide$Site_habitat)

@@

# remove non-algae columns with subset
algae_wide_2 <- comb_wide[ , -which(names(comb_wide) %in% not_algae)]

>>>>

#do we have data for all transects?

comb_wide_quad_sum %>%
  dplyr::group_by(Year, Site) %>%
  dplyr::summarise(count = n())

#should be 200 per year per site (50 at each habitat * 4 habitats)
#2005 and 2006 are one large collective survey
#2021 sites are at 100 (did not do forereef habitats due to COVID)

#do all quads = 100 ?

@@

comb_wide_quad_sum %>%
 dplyr::filter(row_sums != 100) %>% dplyr::filter(Year == 2020)

@@

#yay, they are the same 85

```
```{r}

test <- comb_wide_quad_sum %>%
  dplyr::group_by(Year, Site, Habitat, Transect) %>%
  dplyr::summarise(sum = sum(Quadrat))

test <- comb_wide_quad_sum %>%
  dplyr::group_by(Year, Site, Habitat) %>%
  dplyr::summarise(sum = sum(Transect))

test <- comb_wide_quad_sum %>%
  dplyr::group_by(Year, Site) %>%
  dplyr::summarise(count = n())

unique(test$sum)

test <- comb_wide_quad_sum %>%
  dplyr::group_by(Year) %>%
  dplyr::summarise(sum = sum(Transect))

test <- wide_alldata_filtered %>%
  dplyr::group_by(Year, Site, Habitat) %>%
  dplyr::summarise(count = n())

nique(comb_wide_quad_sum$Year)

sum(test$sum)

(1*10) + (2*10) + (3*10) + (4*10) + (5*10)

@@

```{r filtered data QA QC}
# you can use this to see which sites lost quads during filtering process 
#should be 50 per year/site/habitat combo

wide_alldata_filtered %>%
  dplyr::group_by(Year, Site, Habitat) %>%
  dplyr::summarise(count = n())

wide_alldata_filtered %>%
  dplyr::group_by(Year, Site) %>%
  dplyr::summarise(count = n())

## Anything below this line was to help identify missing data, overall taxa levels, etc. and does not necessarily need to be run to get a cleaned dataframe

@@

### NOTE - USED CHAT GPT FOR THIS NEXT PART
# Step 1: Create a contingency table of counts for each combination of year and site
year_site_counts <- table(comb_wide$Year, comb_wide$Site_habitat)

@@
